---
title: "ass3"
author: "me and my minions"
date: "December 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# installations
```{r}
#install.packages("igraph")
#You might also need
#install.packages("digest")
#install.packages("rgl")
```

# read data

```{r}
# Read the data from the file
library(igraph)

ga.data <- read_csv("~/ass3/ga_edgelist.csv")
g <- graph.data.frame(ga.data,directed = F)
```

# the plot

```{r}
plot(g, vertex.size=10, asp=FALSE)
```


# part 1

## a.

### i.	Betweenness

```{r}
betw <- betweenness(g)
high.betw <- which.max(betw)
betw[high.betw]
```

### ii.	Closeness

```{r}
clos <- closeness(g)
high.clos <- which.max(clos)
clos[high.clos]
```

### iii.	Eigenvector

```{r}
eigen <- eigen_centrality(g)
list.eigen <- eigen$vector
high.eig <- which.max(list.eigen)
list.eigen[high.eig]
```

## b.

### Girvan-Newman

#### i.

##### calculate edge betweeness

```{r}
gc.GN <-  edge.betweenness.community(g)
```

##### assing cluster ID to each person

```{r}
memb.GN <- membership(gc.GN)
```

##### set node colors

```{r}
plot(g, vertex.size=9.7, #vertex.label=NA,
     vertex.color=memb.GN, asp=FALSE)
```

#### ii.

##### the number of communities
```{r}
length(sizes(gc.GN))
```

##### how much members are in every community

```{r}
df.GN = data.frame(sizes(gc.GN))
colnames(df.GN) <- c("Community", "Size")
df.GN
```

#### iii.

##### modularity.

```{r}
gc.GN$modularity
```

##### max modularity

```{r}
max(gc.GN$modularity)
```


### walktrap

#### i.

##### calculate edge betweeness

```{r}
gc.WT <-  walktrap.community(g)
```

##### assing cluster ID to each person

```{r}
memb.WT <- membership(gc.WT)
```

##### set node colors

```{r}
plot(g, vertex.size=9.7, #vertex.label=NA,
     vertex.color=memb.WT, asp=FALSE)
```

#### ii.

##### the number of communities
```{r}
length(sizes(gc.WT))
```

##### how much members are in every community

```{r}
df.WT = data.frame(sizes(gc.WT))
colnames(df.WT) <- c("Community", "Size")
df.WT
```

#### iii.

##### modularity.

```{r}
gc.WT$modularity
```

##### max modularity

```{r}
max(gc.WT$modularity)
```


# part 2 - FACEBOOK

### preperation + Authentication

```{r}
#install.packages("devtools")
library(devtools)

#install_github("Rfacebook", "pablobarbera", subdir="Rfacebook")
 
require("Rfacebook")
 
fb_oauth <- fbOAuth(app_id="375207242939558", app_secret="e6a9e84d51398201b9e01fe29d17251b",extended_permissions = TRUE)
```

### create the funcion that collects the data

```{r}
findConnections<-function(id, token){
  
  nodes.id=1
  nodes.names=1
  nodes.id[1]=id
  nodes.names[1]=getName(id)
  
  edges=1
  
  indexOfNodes=2 #the place we insert to
  indexOfEdges=1
  for(i in 1:75){
    id=nodes.id[i]
    urlPage=makeURL(id)
    dataPage<-callAPI(urlPage, token)$data
    if(length(dataPage)>0){
      for(k in 1:length(dataPage)){
        
        if(indexOfNodes<=75 && any(nodes.id==dataPage[[k]]$id)==FALSE){
          nodes.id[indexOfNodes]=dataPage[[k]]$id
          nodes.names[indexOfNodes]=getName(dataPage[[k]]$id)
          indexOfNodes=indexOfNodes+1
        }
        if(any(nodes.id==dataPage[[k]]$id)){
          edges[indexOfEdges]=nodes.names[i]
          edges[indexOfEdges+1]=getName(dataPage[[k]]$id)
          indexOfEdges=indexOfEdges+2
        }
      }
    }
  }
  graphPages=graph(edges)
  return(graphPages)
}

makeURL<-function(id){
  urlPage<- paste("https://graph.facebook.com/v2.11/",id,"/likes?fields=data",sep = "")
  return(urlPage)
}


getName<-function(id){
  urlPage<- paste("https://graph.facebook.com/v2.11/",id,"?fields=name",sep = "")
  
  return(callAPI(urlPage, token)$name)
}

```

## a.data collection 
we wanted to learn about the relationships of the political pages in Israel.
we used Rfacebook and Facebook API to get the pages that a specefic page liked.
we looped through the pages and extract the likes untill we reached 75 pages.
we started collecting from the facebook page of Benjamin Netanyahu.
we made the graph undirected.

## b. 
nodes: pages on facebook
edges: likes between pages

## c.
```{r}
id=268108602075#Benjamin Netanyahu
token<-"375207242939558|8TdCu1VhRoYxpgULiVAr11CrzFs"
g<-findConnections(id,token)
g<-as.undirected(g)
layout <-
  layout_with_lgl(
    g,
    maxiter = 1000,
    area = length(V(g)) ^ 3.5,
    repulserad = length(V(g)) ^ 5.5
  )

# Draw the plot
plot(
  g,
  layout = layout,
  # vertex.label="",
  vertex.size = 0.1 + 0.75 * sqrt(graph.strength(g)),
  edge.width = 0.01,
  asp = 9 / 16,
  margin = -0.1
)
```

# d.

### a.

#### i.	Betweenness

```{r}
betw <- betweenness(g)
high.betw <- which.max(betw)
betw[high.betw]
```

#### ii.	Closeness

```{r}
clos <- closeness(g)
high.clos <- which.max(clos)
clos[high.clos]
```

#### iii.	Eigenvector

```{r}
eigen <- eigen_centrality(g)
list.eigen <- eigen$vector
high.eig <- which.max(list.eigen)
list.eigen[high.eig]
```

### b.

#### Girvan-Newman

##### i.

###### calculate edge betweeness

```{r}
gc.GN <-  edge.betweenness.community(g)
```

###### assing cluster ID to each person

```{r}
memb.GN <- membership(gc.GN)
```

###### set node colors

```{r}
plot(g, vertex.size=9.7, #vertex.label=NA,
     vertex.color=memb.GN, asp=FALSE)
```

##### ii.

###### the number of communities
```{r}
length(sizes(gc.GN))
```

###### how much members are in every community

```{r}
df.GN = data.frame(sizes(gc.GN))
colnames(df.GN) <- c("Community", "Size")
df.GN
```

##### iii.

###### modularity.

```{r}
gc.GN$modularity
```

###### max modularity

```{r}
max(gc.GN$modularity)
```


#### walktrap

##### i.

###### calculate edge betweeness

```{r}
gc.WT <-  walktrap.community(g)
```

###### assing cluster ID to each person

```{r}
memb.WT <- membership(gc.WT)
```

###### set node colors

```{r}
plot(g, vertex.size=9.7, #vertex.label=NA,
     vertex.color=memb.WT, asp=FALSE)
```

##### ii.

###### the number of communities
```{r}
length(sizes(gc.WT))
```

###### how much members are in every community

```{r}
df.WT = data.frame(sizes(gc.WT))
colnames(df.WT) <- c("Community", "Size")
df.WT
```

##### iii.

###### modularity.

```{r}
gc.WT$modularity
```

###### max modularity

```{r}
max(gc.WT$modularity)
```



